The limits of self commitment and private paternalism \thanks{}

### 2021-01-13 main.tex
Bootstrap chosse_wrong figure

In spite of it high prevalence, pawnshop borrowing has not received much attention in the economics literature. The closest product studied is payday loans. In developing countries, however payday, lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash . According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

@@

We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey before going to the teller window to appraise their piece. The survey was implemented at the entrance of the branch before clients knew the contact that applied that day. It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 7,704 clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
The Appendix \ref{baseline_survey} transcribes the questionnaire in English. Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).

@@

Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important. The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).  
The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a 'non-urgent expense'.
%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),

>>>>

In spite of it high prevalence, pawnshop borrowing has not received much attention in the economics literature. The closest product studied is payday loans. In developing countries, however, payday lending is likely small compared to pawnshop lending; the latter is faster and requires less documentation, allowing access to informal sector workers who receive their salaries in cash. According to \cite{Payday} to get a payday loan: ``All that a prospective borrower typically needs is a home address; a valid checking account; a driver’s license and Social Security number; a couple of pay stubs to verify employment; wages and pay dates; and minimum earnings of at least \$1,000 a month''. Although the author meant this list as an instance of low requirements, they would render virtually all poor households in the developing countries ineligible.

@@

We had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey before going to the teller window to appraise their piece. The survey was implemented at the entrance of the branch before clients knew the contact that applied that day. It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,431 clients (some refused). %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
The Appendix \ref{baseline_survey} transcribes the questionnaire in English. Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).

@@

Since the main treatment involves making clients come to the branch to pay each month, the transaction costs of coming to the branch are important. The average time they take to come to the branch is 22 minutes, and the amount of money they spend in transport to do that is 11 MXN (\$0.60 USD).  
The population we are working with is economically vulnerable in the sense that 30\% of them could not pay either water, electricity \& gas or rent in the past 6 months. They often receive negative income shocks: 87\% said they are pawning because of an emergency, and only 13\% stated it was to use in a `non-urgent expense'.
%When asked why they are pawning this piece \hlgr{5\%} responded \hlgr{`lost a family member'}, \hlgr{`a medical emergency'} (\hlgr{11\%}), \hlgr{`an urgent expense'} (\hlgr{71\%}),
